Secure Composition of Robust and Optimising Compilers

### 2023-06-14 popl/main.tex
Fix floating error

  \item %
        % \Cref{sec:casestud} sets up a case-study to demonstrate the power of our formal framework.
        A case-study demonstrating the power of our formal framework (\Cref{sec:casestud}).
        %We define several different languages and compilers between them and prove that the compilers are robustly preserving different properties.
        To this end, a compilation chain of several passes is presented.
        %The sequential composition of these compilers yields a compilation chain that is optimizing and robustly preserving a combination of \gls{ms} and \gls{cct}.
        The chain attains a combination of \gls{ms} and \gls{cct} by means of applying the theoretical work from the previous contribution on the individual, secure passes concerning \gls{tms}, \gls{sms}, and \gls{scct}, respectively.
        %As for optimizations, the chain has two passes, one performing \gls{cf} and the other \gls{dce}.
        Furthermore, the chain entails two passes for \gls{ms}\MK{maybe patch when optimizing passes are done} that are optimizing: One performs a simple \gls{dce} and the other \gls{cf}.
        %This compilation chain demonstrates the ability to perform modular proof engineering by leaveraging this paper's compositionality theorems.
        This demonstrates that the usage of the presented framework is both simpler and more expressive compared to one monolithic security proof of the whole compilation chain.

>>>>

  \item %
        % \Cref{sec:casestud} sets up a case-study to demonstrate the power of our formal framework.
        A case-study demonstrating the power of our formal framework (\Cref{sec:casestud}).
        %We define several different languages and compilers between them and prove that the compilers are robustly preserving different properties.
        To this end, a compilation chain of several passes is presented.
        %The sequential composition of these compilers yields a compilation chain that is optimizing and robustly preserving a combination of \gls{ms} and \gls{cct}.
        The chain attains a combination of \gls{ms} and \gls{cct} by means of applying the theoretical work from the previous contribution on the individual, secure passes concerning \gls{tms}, \gls{sms}, and \gls{scct}, respectively.
        %As for optimizations, the chain has two passes, one performing \gls{cf} and the other \gls{dce}.
        Furthermore, the chain entails two passes for \gls{ms}\MKin{maybe patch \gls{ms} when optimizing passes are done} that are optimizing: One performs a simple \gls{dce} and the other \gls{cf}.
        %This compilation chain demonstrates the ability to perform modular proof engineering by leaveraging this paper's compositionality theorems.
        This demonstrates that the usage of the presented framework is both simpler and more expressive compared to one monolithic security proof of the whole compilation chain.
